\documentclass[11pt,a4paper,sans]{moderncv}

% ----- ModernCV config -----
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2.6cm}
\usepackage{enumitem}
\setlist[itemize]{topsep=2pt,itemsep=2pt,parsep=0pt,partopsep=0pt}

% ----- Identity -----
\name{Onyero Walter}{Ofuzim}
\title{Robotics \& Autonomy — Controls/Perception}
\address{Calgary, AB}{Canada}{}
\phone[mobile]{+1 403 605 0955}
\social[github]{Waltberry}
\email{onyero.ofuzim@ucalgary.ca}
\social[linkedin]{onyero-walter-ofuzim}

% ----- Document -----
\begin{document}
\makecvtitle

% ===== Professional Summary =====
\section{Professional Summary}
\cvitem{}{Junior controls/estimation engineer with classical/modern control, system ID, and perception fundamentals; ROS/Autoware basics and Python/C++ for prototyping.}


% ===== Core Skills =====
\section{Core Skills}
\cvitem{Controls}{System ID, observers, tuning, trajectory basics}
\cvitem{Perception}{OpenCV pipelines, basic sensor fusion}
\cvitem{Tools}{Python/C++, ROS (foundational), Linux, Git, Docker}
\cvitem{ML}{scikit-learn fundamentals; PyTorch basics}

% ===== Education =====
\section{Education}
\cventry{2025}{M.Sc., Electrical \& Software Engineering}{Schulich School of Engineering, University of Calgary}{}{}{\textit{Focus:} Advanced Control/System Identification, AI (ML/DL), Battery Modeling}
\cventry{2021}{B.Eng., Electrical/Electronic Engineering}{University of Benin, Nigeria}{}{}{\textit{Focus:} Control Systems, Software Engineering}

\vspace{2em}
% ===== Honors & Awards =====
\section{Honors \& Awards}
\cvitem{2024}{Dept. of Electrical \& Software Engineering Funding — University of Calgary}
\cvitem{2024}{International Graduate Tuition Award — University of Calgary}
\cvitem{2024}{Sri Lanka Imanust Graduate Scholarship Engineering Award — UCalgary}
\cvitem{2017}{Federal Government of Nigeria Scholarship}
\cvitem{2016}{Jim Ovia Undergraduate Scholarship — University of Benin}
\cvitem{2016}{Delta State Bursary \& Scholarship — Delta State Government}

% ===== Certifications =====
\section{Licenses \& Certifications}

\cvitem{2025}{\textbf{Snowflake Data Engineering Professional Certificate} — Snowflake}
\cvitem{2025}{\textbf{DeepLearning.AI / AWS Data Engineering Professional Certificate} — DeepLearning.AI}
\cvitem{2025}{\textbf{Docker \& Kubernetes Masterclass (Beginner \textrightarrow{} Advanced)} — Packt}
\cvitem{2025}{\textbf{Mastering Azure Databricks for Data Engineers Specialization} — Packt}
\cvitem{2024}{\textbf{Data Engineer in Python (Career Track)} — DataCamp}
\cvitem{2023}{\textbf{Programming with JavaScript} — Meta \quad|\quad \textbf{Programming in Python} — Meta}
\cvitem{2023}{\textbf{Databases for Back-End Development} — Meta \quad|\quad \textbf{Database Structures \& Management with MySQL} — Meta \quad|\quad \textbf{Advanced MySQL Topics} — Meta}
\cvitem{2023}{\textbf{Introduction to Power BI} — DataCamp}
\cvitem{2022}{\textbf{Big Data Fundamentals with PySpark} — DataCamp \quad|\quad \textbf{Introduction to PySpark} — DataCamp}
\cvitem{2022}{\textbf{Introduction to Airflow in Python} — DataCamp \quad|\quad \textbf{Introduction to AWS Boto in Python} — DataCamp \quad|\quad \textbf{AWS Cloud Concepts} — DataCamp}
\cvitem{2022}{\textbf{Intermediate SQL Server} — DataCamp \quad|\quad \textbf{Intro to Relational Databases} — DataCamp \quad|\quad \textbf{Intro to SQL Server} — DataCamp}
\cvitem{2022}{\textbf{PostgreSQL Summary Stats \& Window Functions} — DataCamp \quad|\quad \textbf{Intermediate SQL} — DataCamp \quad|\quad \textbf{SQL Fundamentals (Skill Track)} — DataCamp}
\cvitem{2022}{\textbf{Machine Learning with scikit-learn / XGBoost / Dimensionality Reduction / Statistical Thinking (Parts 1 \& 2)} — DataCamp}
\cvitem{2022}{\textbf{Cooperation in Autonomous Vehicles} — IEEE \quad|\quad \textbf{Developing \& Validating Control Systems for CAVs} — IEEE}
\cvitem{2022}{\textbf{Python for Data Science and AI (Badge)} — IBM \quad|\quad \textbf{Python for Data Science, AI \& Development} — IBM}
\cvitem{2022}{\textbf{Excel Basics for Data Analysis} — IBM \quad|\quad \textbf{Excel Essentials for Data Analytics (Badge)} — IBM}
\cvitem{2022}{\textbf{Self-Driving Car Fundamentals: Featuring Apollo} — Udacity \quad|\quad \textbf{Introduction to Self-Driving Cars} — University of Toronto}
\cvitem{2021--23}{\textbf{Robotics (Aerial, Motion Planning, Legged Mobility, Perception)} — University of Pennsylvania}
\cvitem{2021}{\textbf{Modern Robotics, Course 1: Foundations of Robot Motion} — Northwestern University}
\cvitem{2021}{\textbf{Machine Learning} — Stanford Online}
\cvitem{2013}{\textbf{Beginner German (CEFR A1)} — Linguaphone}


\vspace{4em}
% ===== Experience =====
\section{Experience}
\cventry{Jan. 2024 -- Present}{Graduate Research/Teaching Assistant}{University of Calgary — DICE Program}{Calgary, AB}{Canada}{
\begin{itemize}
  \item Researched on AI-assisted battery management systems within the Digital Innovation in Clean Energy (DICE) program, contributing to projects aligned with Alberta Innovates’ goals for energy efficiency and sustainability.
  \item Developed and applied methods in system identification, control systems, and AI/ML to support advanced energy storage modeling and optimization.
  \item Served as a Teaching Assistant for multiple courses, including ENEL 469 (Analog Electronic Circuits), ENEL 680 (Applied Optimization for Sustainable Design), ENSF 300 (Software Engineering Practices for Data Management), ENCM 369 (Computer Organization), and ENEL 441 (Control Systems I).
\end{itemize}
}

\cventry{Aug. 2022 -- Nov. 2023}{Lead Technology Specialist / Network Support Analyst}{MTN — NPQA (Network Performance Quality Assurance)}{Lagos, Nigeria}{}{
\begin{itemize}
  \item Progressed from Intern to Lead Analyst within NPQA, leading a team to implement advanced data-driven approaches for network performance optimization.
  \item Developed Python scripts and automated workflows that streamlined monitoring and fault management, reducing manual effort and improving incident response time.
  \item Configured SNMP settings and performed proactive troubleshooting using Linux, Bash, and StableNet, ensuring minimal downtime and maximum network efficiency.
  \item Conducted advanced data analysis and KPI reporting using Python, Excel, and Power BI, providing insights that supported strategic decision-making and contributed to a $\sim$15\% reduction in network downtime (estimated \$500K annual savings).
  \item Collaborated cross-functionally with engineering and operations teams to integrate innovative software solutions, enhance fault detection, and drive continuous network performance improvements.
\end{itemize}
}

\cventry{Jan. 2020 -- Aug. 2021}{Graduate Research Assistant}{University of Benin — Dept. of Electrical/Electronic Engineering}{Benin, Nigeria}{}{
\begin{itemize}
  \item Conducted research in embedded systems and IoT technologies, focusing on developing efficient battery monitoring and management solutions for enhanced energy sustainability.
  \item Designed and prototyped an IoT-enabled remote battery monitoring and control device, enabling improved energy efficiency and demonstrating potential to reduce local energy costs by up to 30\%.
  \item Published findings in \textit{Design and Construction of a Remote Battery Monitoring and Control Device Using the Internet of Things (IoT)} \href{https://www.researchgate.net/publication/369377501_Design_and_Construction_of_a_Remote_Battery_Monitoring_and_Control_Device_Using_the_Internet_of_Things_IoT}{[ResearchGate]}.
\end{itemize}
}

\cventry{Nov. 2019 -- May 2020}{Network Operations/Support Engineering Intern}{MTN --- NSMC}{Lagos, Nigeria}{}{
\begin{itemize}
  \item Gained cross-departmental exposure in NSMC, collaborating with TX/IP MPLS, Data \& Internet Services, and NSS units to support end-to-end network operations.
  \item Monitored network performance using SNMP and other monitoring tools, contributing to proactive fault detection and improved service reliability.
  \item Assisted in incident management and escalation processes, participating in root-cause analysis and ensuring timely problem resolution.
  \item Supported reporting and analytics by preparing daily, weekly, and monthly performance dashboards in Excel, providing data-driven insights for operations teams.
\end{itemize}
}

\cventry{Aug. 2019 -- Nov. 2019}{Automation/Electrical Engineer Intern}{Nigerian Bottling Company (Coca-Cola HBC)}{Lagos, Nigeria}{}{
\begin{itemize}
  \item Assisted the Automation/Electrical Department in maintaining and troubleshooting electrical and electronic systems, ensuring reliable plant operations.
  \item Performed daily machine inspections and quality control checks to identify faults and prevent unexpected downtime.
  \item Assembled, tested, and repaired malfunctioning machinery under supervision, contributing to improved equipment reliability.
  \item Created work orders and compiled plant performance reports using Excel, streamlining documentation and workflow efficiency.
\end{itemize}
}

% \vspace{2em}
% % ===== Selected Projects =====
% \section{Selected Projects}
% \cvitem{E-Commerce Recommender System}{\small Production-ready recommender built with Python \& Streamlit using batch/streaming pipelines. \href{https://github.com/Waltberry/recommender-system}{\color{blue}GitHub}}
% \cvitem{Customer Churn Prediction}{\small Machine learning pipeline for telecom churn modeling. \href{https://github.com/Waltberry/Customer-Churn-Prediction-in-a-Telecom-Company}{\color{blue}GitHub}}
% \cvitem{IoT Battery Monitoring Device}{\small Research prototype for remote battery monitoring \& control. \href{https://www.researchgate.net/publication/369377501_Design_and_Construction_of_a_Remote_Battery_Monitoring_and_Control_Device_Using_the_Internet_of_Things_IoT}{\color{blue}ResearchGate}}
% \cvitem{Fine-Tuned BERT Classifier}{\small NLP text classification with TensorFlow. \href{https://github.com/Waltberry/Fine-Tune-BERT-for-Text-Classification-with-TensorFlow}{\color{blue}GitHub}}
% \cvitem{Stock Monitor}{\small Real-time stock analysis dashboard with Python. \href{https://github.com/Waltberry/StockMonitor}{\color{blue}GitHub}}

% % ===== Job Simulations =====
% \section{Job Simulations} 
% \cvitem{J.P. Morgan Software Engineering Virtual Experience}{\small Built live data visualization dashboards and resolved dev environment issues.}
% \cvitem{Siemens Mobility Project Management Simulation}{\small Designed KPIs \& dashboards for rail infrastructure projects.}
% \cvitem{Ford EV Engineering Simulation}{\small Performed EV battery cost-benefit analysis and PID controller tuning.}
% \cvitem{Blackbird Australia Software Engineering Simulation}{\small Contributed to cloud infrastructure design \& A/B testing features.}

% ===== Footer =====
% \cvitem{}{\small References available upon request.}

\end{document}
